Generate Random Forest Models

### 2023-12-30 scripts/generate_RF_models.Rmd
funs for rf modelling

p <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2'
paths <- list.dirs(p, recursive = T)
paths <- paths[2:length(paths)]
paths <- paths[! grepl('chelsa$|veg_cover$|soilgrids$|sand$|silt$|clay$|phh2o$|cfvo$', paths) ]

@@

layers <- lapply(files, vrt)
layers <- rast(layers)
names(layers) <- basename(paths)
```

@@

abvi <- filter(train_dat, taxon == 'Abronia villosa')

abvi_test <- terra::extract(layers, abvi)

# identify a single component of each pair for usage. 
```

>>>>

p <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2'
paths <- list.dirs(p, recursive = T)
paths <- paths[2:length(paths)]
paths <- paths[! grepl('chelsa$|veg_cover$|soilgrids$|sand$|silt$|clay$|phh2o$|cfvo$|soc$', paths) ]

@@

layers <- lapply(files, vrt)
layers <- rast(layers)
names(layers) <- basename(paths)

rm(paths, files)
```

@@

splicies <- split(train_dat, f = train_dat$taxon)

cores <- parallel::detectCores()
lapply(splicies[3:335], modeller)

```
